The \dealii Library, Version 9.7

### 2025-08-19 9.7/paper.tex
rename folder
Minor edits.

\begin{figure}[hb]
\includegraphics{kokkos-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{kokkos-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature
  matrix assembly, right: temperature right-hand side assembly)
  comparing TBB and Taskflow with and without coloring (corresponding
  to ``Implementation 2'' and ``Implementation 3'' in \cite{TKB16}).}
\label{fig:tbb-vs-taskflow}
\end{figure}

>>>>

\begin{figure}[hb]
\includegraphics{taskflow-vs-tbb/plots-figure1.pdf}\hfill
\includegraphics{taskflow-vs-tbb/plots-figure2.pdf}
\caption{Assembly times in a modified step-32 (left: temperature
  matrix assembly, right: temperature right-hand side assembly)
  comparing TBB and Taskflow with and without coloring. These figures
  correspond to the middle row of \cite[Fig. 4]{TKB16}. Lines with
  squares match ``Implementation 2'' in \cite{TKB16}; the lines with
  circles labeled ``colored'' match ``Implementation 3'' therein.}
\label{fig:tbb-vs-taskflow}
\end{figure}
